\chapter*{\centering{\large{ABSTRACT}}}

\begin{spacing}{1}
\textbf{MUHAMMAD ARDANI}. Android-Based Wound Assessment Application Integrated with the Wound Care Clinic Information System. Thesis. Computer Science Study Program, Faculty of Mathematics and Natural Sciences, Universitas Negeri Jakarta. 2025. Supervised by Muhammad Eka Suryana, M.Kom, and Drs. Mulyono, M.Kom.
\newline
\newline
\textit{The causes of chronic wounds and the factors influencing wound healing are quite complex and diverse. In the process of diagnosing, treating, and managing chronic wounds, doctors and nurses need to have a comprehensive understanding, complete medical records, effective management, and timely monitoring of the patient's general physical condition, laboratory examination reports, wound assessment, and fractional wound treatment. In general, wound assessment is still carried out traditionally using paper-based recording or archiving methods. Currently, this data is still recorded manually, which poses a risk of calculation errors. Moreover, previous research lacked an accurate assessment of chronic wound evaluation data. Therefore, this study aims to develop a chronic wound assessment application with the Bates-Jensen Assessment Wound Tools (BWAT) module based on Android. The assessment data used in this study focuses on recording patients undergoing chronic wound treatment. The system development process follows the Scrum methodology, and the entire application is built using the Kotlin programming language while integrating findings from previous research. The final result of this study is a wound assessment application that assists nurses in documenting the wound healing process and enables patients to track their own healing progress.}
\newline
\newline
\noindent \textbf{\textit{Key}}: \textit{android, application, chronic wounds, BWAT, Scrum, documentation, integration}
\end{spacing}